---
title: "HW_Report"
author: "junlakiat"
date: "2023-03-03"
output:
  pdf_document: default
  html_document: default
---

## Homework

Explore dataframe `diamonds` and create 5 visualizations.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(patchwork)
set.seed(36)
diamonds_sam <- diamonds %>% sample_frac(0.2)
head(diamonds)
```

### Chart 1 - relationship between carat and price.

```{r message=FALSE, warning=FALSE}
c1 <- ggplot(diamonds_sam, aes(carat, price)) +
  geom_point() +
  geom_smooth() +
  theme_minimal()
c1
```
We found a positive relationship between two variables.

## Chart 2 - Bar chart of diamond cuts.
```{r message=FALSE, warning=FALSE}
c2 <- ggplot(diamonds_sam, aes(cut, fill = color)) +
  geom_bar(position="fill") +
  theme_minimal()
c2
```

## Chart 3 - Histogram of diamond prices.
```{r message=FALSE, warning=FALSE}
c3 <- ggplot(diamonds_sam, aes(price)) +
  geom_histogram(fill = "#0066CC", color = "black")+
  theme_minimal()
c3
```
This diamond’s Price has skew distribution on to the right. Most of the diamonds cost about $300 to $6,000.

## Chart 4 -Scatter plot of diamond prices by carat and clarity.
```{r message=FALSE, warning=FALSE}
c4 <- ggplot(diamonds_sam, aes(carat, price)) +
  geom_point(aes(color = clarity))+
  geom_smooth()+
  theme_minimal()
c4
```
Low carat has high clarity IF more than High carat.
Price of low carat has high clarity not most high carat has low clarity. 

## Chart 5 - Faceted scatter plot of diamond prices by carat and cut.
```{r message=FALSE, warning=FALSE}
c5 <- ggplot(diamonds_sam, aes(carat, price, color = color)) +
  geom_point() +
  facet_wrap(~cut)+
  theme_minimal()
c5
```

```{r message=FALSE, warning=FALSE}
c1/c2/c3
```
```{r message=FALSE, warning=FALSE}
c4/c5
```

